Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-27 writeup/gz_hubble_data.tex

\begin{figure*}
\includegraphics[width=160mm]{figures/gzh_interface.png}
\caption{Screenshot of the Galaxy Zoo: Hubble interface showing an example COSMOS image at the first step in the decision tree.\label{fig:interface}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{}
\label{fig:decisiontree}
\end{center}
\end{figure*}

@@

>>>>

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/gzh_interface.png}
\caption{Screenshot of the Galaxy Zoo: Hubble interface showing an example COSMOS image at the first step in the decision tree.\label{fig:interface}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH users, labeled with the corresponding Task numbers. Tasks in the decision tree are color-coded by tier level: Gray-colored Tasks are 1st tier questions which are asked of all users. Tasks colored green, blue, purple, and pink (respectively) are one, two, three, or four steps below branching points in the decision tree.}
\label{fig:decisiontree}
\end{center}
\end{figure*}

@@

\subsubsection{COSMOS}

The COSMOS galaxies have several published datasets automatically classifying their morphologies, all using a variation of non-parametric measurements clustered with machine algorithms and trained on a visually-classified reference set of several hundred galaxies. \citet{cas07} use a combination of $C$, $A$, $G$, and $M_{20}$ \citep{cas05} to classify all galaxies with $m_\mathrm{I,petro}<25$. They divide galaxies into three broad morphological categories: early-type, spirals, and irregulars. A very similar method is employed by \citet{tas11}; they use the same non-parametric indices to determine galaxy morphology, but with a slightly different method of calculating the Petrosian radius. 64\% of the galaxies have identical classifications in \citet{cas07} and \citet{tas11}; roughly two-thirds of the disagreements are galaxies originally classified as ``irregular'' in \citet{cas07} but ``spiral'' in \citet{tas11}.

Using a 0.5\arcsec{} positional match, we find 76,241 galaxies with morphologies in both GZH and \citet{cas07}. At the lowest values of \pbest, $\sim10\%$ of the \citet{cas07} galaxies are classified as irregular, only $\sim30\%$ as early-type, and $60\%$ as spiral. The early-type fraction drops with increasing \pbest, with an increasing proportion of irregulars. The \podd{} vote fraction distinguishes sharply between spirals and irregulars at \podd$>0.2$.

Despite using a similar classification method to \citet{cas07}, the \citet{tas11} classifications show significantly different trends as a function of GZH classifications. Spiral galaxies consistently make up $\sim60\%$ of the sample at \emph{all} \pbest, with a mild increase at \pbest$\simeq1.0$. Early-type and irregular galaxies make up the remainder, smoothly varying between irregulars at low \pbest{} and early-types and high \pbest.

% Show the fraction of galaxies in each category as a function of p_features and p_odd?
